My title

### 2023-03-14 outputs/paper/paper.qmd
Added table that shows a subset of the key features of our cleaned dataset.

```{r}
#| echo: false
# Summary statistics of our GSS data 
summ_gss <- cleaned_2016gss_data %>% 
  select(age, sex, race, income, rincome, 
         degree, childs, marital,
         happy, wwwhr)
# sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
## the final line doesn't w
#ork for some reason and i'm mad
```

>>>>

```{r}
#| echo: false
# ATTEMPT: Summary statistics of our GSS data 
# summ_gss <- cleaned_2016gss_data %>% 
#   select(age, sex, race, income, rincome, 
#          degree, childs, marital,
#          happy, wwwhr)
# sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
## the final line doesn't work for some reason and i'm mad

# Table showing the first 10 rows of our cleaned dataset 
cleaned_2016gss_data |>
  select(age, sex, race, 
         degree, childs, marital,
         happy, wwwhr) |> 
  slice(1:8) |> 
  kable(caption='A subset of key features',
        col.names = c("Age", "Sex", "Race", "Highest Degree", 
                      "Number of Children", "Marital Status", "Happiness Level", 
                      "Weekly Internet Hours"),
        digits = 1,
        booktabs = FALSE,
        linesep = "") |>
  kable_styling(full_width = T)
```
